	\begin{frame}
		\frametitle{TABLE OF CONTENTS}
		\begin{itemize}
			\item INTRODUCTION
			\item OBJECTIVES
			\item LITERATURE REVIEW
			\item METHODOLOGY
			\item RESULTS
			\item DISCUSSION
			\item CONCLUSION
			\item RECOMMENDATIONS
			\item REFERENCES 
		\end{itemize}
	\end{frame}
\begin{frame}
\frametitle{Introduction}
\begin{itemize}
	\item Malnutrition is defined as imbalance, deficiencies, or excess nutrients intake. It is classified as undernutrition or overnutrition
	\item Undernutrition has been looked at as either stunting (low height for age), underweight (low weight for age), deficiencies in vitamins and minerals, and wasting (low weight for height) (Fact Sheets - Malnutrition, 2021; Kenya: Nutrition Profile, 2021).
	\item Proper nutrition is a crucial factor in children’s growth and development. The first two years are foundational for proper mental health, optimal physical, cognitive growth, and development.
\end{itemize}
	\end{frame}
\begin{frame}
	\frametitle{PROBLEM STATEMENT}
	\begin{itemize}
		\item Globally, malnutrition contributes to half of the under-five deaths, with Africa leading at 51\%, Asia 41\%, and the rest of the world at 8\% (Shah, 2020).
		
		\item In Kenya, malnutrition rates are a cause for concern, with high numbers in certain regions. It exposes children to various infections, which complicate the outcome (Bain et al., 2013). 
		
		\item Results from the Kenya Demographic Health Survey (2014/2015) indicate that approximately 26\% of the children under five are stunted, 4\% are wasted, and 11\% are underweight.  
		
		\item Poorly nourished children suffer up to 160 days of illness annually(de Vita et al., 2019). 
		
		\item Additionally, malnutrition worsens infections by reducing the body’s ability to convert food to nutrients.
		
		\item Therefore, identifying malnutrition determinants is indispensable in achieving Good Health and Well Being, Zero Hunger, and Food Security and Nutrition. 
	\end{itemize}
\end{frame}
\begin{frame}
\frametitle{RESEARCH QUESTIONS}
\begin{itemize}
	\item What is the prevalence of malnutrition among children under 5 in Kenya? 
	\item Is there an association between socio-economic characteristics and under-five malnutrition?
	\item Is there an association between bio-demographic characteristics and under-five malnutrition?
	\item What factors are associated with under-five malnutrition in Kenya? 
	
\end{itemize}
\end{frame}
\begin{frame}
\frametitle{JUSTIFICATION}
\begin{itemize}
	\item 	Malnutrition has adverse effects on children during their early stages of development and growth. 
	\item It reduces their immunity, making them susceptible to different severe infections.
	\item Literature has shown wanting statistics of malnutrition that calls for action hence the purpose of our study. 
	\item This study is aimed at providing awareness of the factors associated with malnutrition among children under five.
	\item This study will help the government make and implement policies to reduce malnutrition, which enables them to achieve the Big 4 Agenda and the SDGs. 
\end{itemize}
\end{frame}
