	\begin{frame}
		\frametitle{LITERATURE REVIEW}
		\begin{itemize}
			\item Several policies and measures have been put in place in the country to address the issue of malnutrition. \textcolor {blue} {Although these policies have helped counter the rising rate of malnutrition, cases are still persistent.} 
			\item Socioeconomic factors associate social and economic factors. They are lifestyle elements and measurements of both social standing and financial viability. These include: \textcolor {blue} {maternal nutrition, maternal education, wealth index} and \textcolor {blue} {place of residence.}
			\item Bio-demographic factors are factors in which biological considerations such as evolutionary, epidemiological and genetic determinants are accentuated. Child health and survival can be affected by alterations in reproductive patterns through various mechanisms, more so through changes in; \textcolor {blue} {birth order, maternal age at birth or birth intervals} (Sathiya Susuman et al., 2016).
		
		\end{itemize}
	\end{frame}

\begin{frame}
	\frametitle{PREVALENCE VS ODDS RATIO}
	\begin{itemize}
		\item In most medical and epidemiological studies, Relative Risk is always the parameter of interest. It is estimated when the study focuses on measuring the association between exposure and outcome.
		\item Usually, when the outcome variable is dichotomous, the appropriate statistical technique to use is Logistic regression which gives Odds Ratio (Zou, 2004). 
		\item In Cross-sectional studies, Prevalence ratio and Prevalence Odds Ratio are used to measure the association between exposure and outcome. Risk Ratio is more appropriate in this type of study and can be computed from Prevalence ratio (McNutt et al., 2003). 
		\item Odds ratio can be interpreted as risk ratio when the outcome of interest is rare or when the incidence is below 10\% (McNutt et al., 2003). 
		\item Nevertheless, when the outcome of interest is common or when the prevalence is more than 10 percent (Cummings, 2009), interpreting Odds Ratio as Relative risk can highly overestimate the effect. 
	\end{itemize}
\end{frame}
